Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-14 Thesis/chapter/03-theoretical-background.tex
wiki thesis
refine sputtering

%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\ds{what is it? What is it used for? How does it work? What different kinds are there? }
\ds{
\todo{Structure: Free writing} 
Ueber das Material, also PV und speziell CIGS (copper indium gallium sulfide) 
ueber den MC prozess berichten, also DB, i-v curven, sputtering, sem, ir, xrd
ueber den it ml stuff und statistisch, also ML algemein, pso im speziellen 
perfekt fuer intro einfach mal erwaehnen was wo in diesem capitel zu finden sein wird. 
Books PV, analytic otto? 
}
This chapter can be broken down into three section. 
The first chapter tries to shine light on the evolution of PV and give some background on \gls{cigs}.
The second chapter reads about material-scientific methods which were used during the practical part of this work. 
The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties. 
%This chapter aims to shine light on the evolution of PV and on CIGSand 
%give some introduction on methods used during experimental and \td{analytical} phase of this work. 
\subsection{Photovoltaics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored. 
Even though this time period is not exact and highly dependent on detection methods, 
this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
One viable options is \gls{pv}.

@@

\subsubsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilzed down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage due to phase transition\cite{Nielsen2005}.
%\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
It is not poisonous. \td{cite?}
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
See ref \cite{Nielsen2005} for 2.3 Hydrous Zirconium Oxide 2.3 and 2.20 Zirconium Alkoxides.

\td{what is important properites of zro2? }
\td{what is it? What is it used for? How does it work? What different kinds are there? }

@@

\subsection{Sputtering}
% https://en.wikipedia.org/wiki/Sputter_deposition
\td{what is the principle behind sputtering
what is sputtering, how does it work, what different kinds of sputtering is there, 
what is is used for? 
what was it used for in this work? 
}
\td{
- phenomon of high energy particle bombardement know off particles from a source
- options to create high energy particles: electron gun, thermal evaporation or cathode? 
- vorteile sind: Swann p 67(2)
- need low pressure bcs of MFP but plasma needs gas to sustain
- source is target and target is substrate
}
%Sputtering is a physical deposition method. 
Sputtering describes the process of particles being sputtered from a surface after 
impact of highly energetic particles.
These high energy particles start cascades of momentum transfers. 
If a path of a cascade reaches back to the surface and the kinetic energy of a surface 
particle exceeds the binding energy, it is ejected (or sputtered).

%Sputtering describes the process when highly energetic particles collide with a surface 
%and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
This process occurs naturally in outer space (through alpha particles, electrons etc.) 
and is used in science and technology for 
sputter cleaning, thin film deposition, analysis or etching. 
The phenomenon was discovered and identified as an atomic collision phenomenon in the 
middle of the 20th century and now is a field of research with its own niche subfields 
(e.g. sputtering of exotic materials (such as condensed gases, planetary
atmospheres, lunar dust grains, proteins and viruses), high density cascades and 
linear cascades, which could be called classical sputtering)
%sputtering of insulators and biomolecular material)
\cite{Sigmund1987}.
%
In this work it was used to deposit thin gold contacts through a mask. 
A directional current sputtering machine was used. 
\td{describe the machine}
A argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
Argon ions are accelerated through the field to the source (a metal wafer), which acts as cathode, and start cascades. 
In order to maximise the yield (sputtering speed) a magnet is used to trap the plasma close to source. 
Plasma sputtering with a strong magnet to 
1.5h 
\\
\td{A high voltage is angelegt at the source (a metal wafer). 
Electrons with a high kinetic energy bump into the source and herausschießen metal atoms, 
which will deposit on a target. 
By ausrüsten the target with a mask, arbitrary musters can be obtained (e.g. contact arrays).
}
How are the electrons erzeugt? 
\td{With a magnetron (a micro wave erzeuging high vacuum bauteil) a plasma is sustained. 
}
Find source\\\\

SPUTTERING FREEWRITING: 
what is sputtering? \\
sputtering is the processes of highly energetic ions (only ions?) hitting a surface and atoms or molecules being expelled. 
This is a physical vapor deposition technique (PVD). PVD can be unterteils in thermal and highly energetic activated. Sputtering is part of HEA, which hast the convenience, that some substrates don't withstand high temperatures. 
what can it be used for?\\
Sputtering moved from being a curious experiment to having multi anwendungen in science (forschung) and engineering, becuase the sputtered materials can be deposited on  substrate. 
anwendungen reichen from, thin films for PV, electrical circuits, storage media such as CDs and DVDs etc. 
Vorteile of sputtering are also a good adherent to the substrate and good step coverage and what else? 
different styles\\
The most successful durchgesetzte kind of sputtering devices are magnetron sputtering devices, which wiederum can be unterteilt in DC (directional current) RF (radio frequency) sputtering and reactive sputtering. 
how does it work? \\
A high voltage is applied to the source (make skizze), which acts as a cathode. 
The cathode, then, emits electrons which collide with XXX gas (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
The argon may get ionized by electron and the argon cation will be accelerated to the cathode. If the cation has enough energy it will bump off a target atom or molecule. 
This happens by a cascade of momentum transfers, which can reach the surface again. 
If the suface particle gets momentum pointing from the surface and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
The pressure should be small, such that the sputtered particle has a moeglichst long mean free path (MFP), but on the other hand there is a minimum pressure to keep the plasma going. 
Usual pressures are around (1 mPa?).
\td{mention the substrate parallel to the target}

A magnetron can be placed behind the cathode (target) in order to trap ejected ions close to the electron source. 
This prevents high energy electrons from reaching the target and undoing the deposited layer and increasing the probability of an electron colliding with an argon atom and ionizing it

>>>>

%\url{https://link.springer.com/content/pdf/10.1186/2228-5326-3-8.pdf}
\ds{what is it? What is it used for? How does it work? What different kinds are there? }
\ds{what? how? why?}
\ds{
\todo{Structure: Free writing} 
Ueber das Material, also PV und speziell CIGS (copper indium gallium sulfide) 
ueber den MC prozess berichten, also DB, i-v curven, sputtering, sem, ir, xrd
ueber den it ml stuff und statistisch, also ML algemein, pso im speziellen 
perfekt fuer intro einfach mal erwaehnen was wo in diesem capitel zu finden sein wird. 
Books PV, analytic otto? 
}
This chapter can be broken down into three section. 
The first chapter tries to shine light on the evolution of PV and give some background on \gls{cigs}.
The second chapter reads about material-scientific methods which were used during the practical part of this work. 
The last and third part focuses on the information technological, algorithmic and analytics methods used to optimize and predict material properties. 
%This chapter aims to shine light on the evolution of PV and on CIGSand 
%give some introduction on methods used during experimental and \td{analytical} phase of this work. 
\subsection{Photovoltaics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Problems of current energy supply}
The world wide energy consumption has more than doubled between 1970 and 2015\cite{BP2017} 
and according to recent studies both fossil\cite{BGR2017} and uranium sources\cite{Uran2006} 
will be exhausted within the next 100 years. 
%This time period must of course taken with a grain of salt as it can happen that even though the resource are being exhausted they can rise from one year to another as new reserves are being discovered and explored. 
Even though this time period is not exact and highly dependent on detection methods, 
this number is rather small and brings us in zugzwang to develop sustainable energy sources. 
One viable options is \gls{pv}.

@@

\subsubsection{Zirconium oxide}
Zirconium oxide \gls{zro} is a ceramic with a band gap of 5-7 eV and dielectric constant of 15-22 at room temperature\cite{Anwar2017}. 
This makes it attractive as an insulator for semiconductor and \gls{pv} industry. 
It is monoclinic below 1050 °C, tetragonal between 1170 °C and 2370 °C, and cubic above 2370 °C\cite{Nielsen2005}.
The cubic phase can be stabilzed down to room temperature by the addition of magnesia (\ch{MgO}), calcia (\ch{CaO}) or yttria (\ch{Y2O3}) which avoids mechanical failing due to shrinkage 
when cooling and undergoing phase transistion\cite{Nielsen2005}.
%due to phase transition\cite{Nielsen2005}.
%\td{[R. Stevens, 1986. Introduction to Zirconia. Magnesium Elektron Publication No 113]}
%Ralph Nielsen "Zirconium and Zirconium Compounds" in Ullmann's Encyclopedia of Industrial Chemistry, 2005, Wiley-VCH, Weinheim. doi:10.1002/14356007.a28_543
%It is not poisonous. \td{cite?}
It is very resistant to acids (except \ch{HF} and hot \gls{h2so4}) and alkalis\cite{Nielsen2005}.
%See ref \cite{Nielsen2005} for 2.3 Hydrous Zirconium Oxide 2.3 and 2.20 Zirconium Alkoxides.
Hydrous Zirconium Oxide (\ch{Zr(OH)8 * 16 H2O}) gel can be produced by neutral hydrolysis of sodium zirconate (\ch{NaZrO3}). 
"Zirconium alkoxides hyrdolize quite easily, [providing] a route to high purity, high-surface-area zirconium oxide"\cite{Nielsen2005}.

%\td{what is important properites of zro2? }
%\td{what is it? What is it used for? How does it work? What different kinds are there? }

@@

\subsection{Sputtering}
% https://en.wikipedia.org/wiki/Sputter_deposition
\iffalse
\td{what is the principle behind sputtering
what is sputtering, how does it work, what different kinds of sputtering is there, 
what is is used for? 
what was it used for in this work? 
}
\td{
- phenomon of high energy particle bombardement know off particles from a source
- options to create high energy particles: electron gun, thermal evaporation or cathode? 
- vorteile sind: Swann p 67(2)
- need low pressure bcs of MFP but plasma needs gas to sustain
- source is target and target is substrate
}
%Sputtering is a physical deposition method. 
Sputtering describes the process of particles being sputtered from a surface after 
impact of highly energetic particles.
These high energy particles start cascades of momentum transfers (see figure \td{cp sigmund 1969}). 
If a path of such a momentum transfer cascade reaches back to the surface and the kinetic energy of a surface 
particle exceeds the binding energy, it is ejected (or sputtered).

%Sputtering describes the process when highly energetic particles collide with a surface 
%and through a cascade of momentum transfers surface particles are depleted and sputter from the surface.
This process occurs naturally in outer space (through alpha particles, electrons etc.) 
and is used in science and technology for 
sputter cleaning, thin film deposition, analysis or etching. 
The phenomenon was discovered and identified as an atomic collision phenomenon in the 
middle of the 20th century and is now a field of research with its own niche subfields 
(e.g. sputtering of exotic materials (such as condensed gases, planetary
atmospheres, lunar dust grains, proteins and viruses), high density cascades and 
linear cascades, which could be called classical sputtering)
%sputtering of insulators and biomolecular material)
\cite{Sigmund1987}.
%
In this work it was used to deposit thin gold contacts through a mask. 
A directional current sputtering machine was used. 
\td{describe the machine}
An argon plasma in a strong electrical field (some kV) provides the highly energetic particles. 
Argon ions are accelerated through the field to the source (a metal wafer), which acts as cathode, and start cascades. 
In order to maximise the yield (sputtering speed) a magnet is used to trap the plasma close to source. 
Plasma sputtering with a strong magnet to 
1.5h 
\\
\td{A high voltage is angelegt at the source (a metal wafer). 
Electrons with a high kinetic energy bump into the source and herausschießen metal atoms, 
which will deposit on a target. 
By ausrüsten the target with a mask, arbitrary musters can be obtained (e.g. contact arrays).
}
How are the electrons erzeugt? 
\td{With a magnetron (a micro wave erzeuging high vacuum bauteil) a plasma is sustained. 
}
Find source\\\\
\fi

%SPUTTERING FREEWRITING: 
%what is sputtering? \\
Sputtering is the processes of highly energetic ions hitting a surface and atoms or molecules being expelled. 
This is called a physical vapor deposition (PVD) technique. 
PVD can be divided into activation by thermal energy and activation by energetic particle bombardment. %\td{high-energy particles}.
%thermal and highly energetic particles activated. 
Sputtering is of the latter, which 
is advantageous if substrates can't withstand high temperatures.
%has the convenience, that some substrates can't withstand high temperatures. 
%\td{what can it be used for?}\\
Sputtering evolved from being a curious experiment in the middle of the 20th century to having various applications in research and engineering.
Use cases vary from thin films depositions for \gls{pv}, for electrical circuits or for storage media such as CDs and DVDs 
over sputter cleaning and etching to analysis.
Advantages of 
sputtered thin films include good adhesion to the substrate and good step coverage. 
%sputtering are also a good adherent to the substrate and good step coverage and what else?

%\td{how does it work?}\\
A high voltage is applied to 
two parallel electrode with low pressure gas in between. 
The target acts as cathode and the substrate (holder) as anode (see \td{fig}).
%the target which acts as a cathode with the substrate as anode in a parallel geometry (see \td{fig}).
%(the substrate represents the anode). 
The cathode, then, emits electrons which collide with a gas particle (mostly argon because of it's inert properties and potential to transfer more kinetic than lighter noble gases). 
Some gas particles may get ionized by the collision and the gas cation is accelerated to the cathode. 
If the cation has enough energy it will bump off a target atom or molecule from the surface. 
This happens by a cascade of momentum transfers, which can reach the surface again (see fig \td{cp sigmund69}). 
If the surface particle gets momentum pointing away from the bulk and the remaining kinetic energy is higher then the binding energy, the particle is sputtered. 
The pressure should be small, such that the sputtered particle has a long mean free path (MFP), but on the other hand there is a minimum pressure to keep the plasma going. 
Usual pressures are around 1 mPa (1 mbar) or lower\cite{Swann}.

A magnetron can be placed behind the cathode (target) in order to trap ejected electrons close to the source. 
This prevents high energy electrons from reaching the target and undoing the deposited layer and this also increases the probability of an electron colliding with an argon atom and ionizing it.

When oxygen or nitrogen are added to the  gas this is called reactive sputtering.
Sputtered atoms will react with the gas and result in oxide or nitrides layers, respectively.
The stoichiometry of the resulting layer can be regulated by gas ratios, but too much reactive gas can lead to target poisoning\td{cite? What is poisoned?}.

The limitation of only being able to use conducting materials as targets can be circumvented by using a radio frequency electrical field. 
This prevents a charge building up on the target. \td{why is a charge?}
Although RF sputtering is more versatile, DC sputtering is more common because of it's simpler system and economical reasons.
%Through this method only conducting materials can be sputtered, be
\td{sputtered particles are neutral and not influenced by the electrical field}
%\td{different styles}\\
%The most successful/common/established type of sputtering devices are magnetron sputtering machines, which 
%Sputtering devices can be separated in DC (directional current) and RF (radio frequency) sputtering and reactive sputtering. 
%During RF sputtering, the voltage is wobbling which prevents charge accumulation on the target and thus also non conduction targets can be sputtered.
